Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
references for Boehm already introduced before.
some more reference and tweaks

More precisely, it is usually possible to deduce information about the
result variable of an operation given information about its arguments.
For example, we can say that the addition of two integers must be an
integer.  Most programming languages have this property.  However,
Python -- like many languages not specifically designed with type
inference in mind -- does not possess a type system that allows much
useful information to be derived about variables based on how they are
\textit{used}; only on how they were \textit{produced}.  For example, a number of very
different built-in types can be involved in an addition; the meaning of
the addition and the type of the result depends on the type of the input
arguments.  Merely knowing that a variable will be used in an addition
does not give much information per se.  For this reason, our annotator
works by flowing types forward, operation after operation, i.e.\ by
performing abstract interpretation of the flow graphs.  In a sense, it
is a more naive approach than the one taken by type systems specifically
designed to enable more advanced inference algorithms.  For example,
Hindley-Milner type inference works in an inside-out direction, by
starting from individual operations and propagating type constraints
outwards [H-M].

@@

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a [Dhrystone] 2.0
derivative traditionally used by the Python community, although it is
a rather poor benchmark) and the classical [Richards] benchmark and
compared against [CPython] 2.4.3 results and are summarized in table
\ref{perfsumm}.

@@

{\bf pypy-c.}
    The simplest variant: translated to C code with no explicit memory
    management, and linked with the Boehm conservative GC [Boehm].

@@

The resulting generating extension will be essentially similar to
[Psyco], which is the only (and hand-written) JIT available for Python so
far, based on run-time specialization.

@@

Jikes RVM \cite{DBLP:journals/ibmsj/AlpernABBCCCFGHHLLMNRSSSSSSW00} is a
Java VM and Just-In-Time compiler written in Java.
Bootstrapping happens by self-applying the compiler on a host VM, and
dumping a snapshot from memory of the resulting native code.
This approach directly enables high performance, at the price of
portability -- as usual with pure native code emitting
approaches. Modularity of features, when possible, is achieved with
normal software modularity. The indirection costs are taken care of by
the compiler performing inlining (which is sometimes even explicitly
requested).  In particular this modular approach is used
for implementing a range of choices for GC support \cite{JikesGC}.  This was
the inspiration for PyPy's own GC framework, although much more tuning
and work went into Jikes RVM.  PyPy's own GC framework also exploits
inlining of helpers and barriers to recover performance.

>>>>

More precisely, it is usually possible to deduce information about the
result variable of an operation given information about its arguments.
For example, we can say that the addition of two integers must be an
integer.  Most programming languages have this property.  However,
Python -- like many languages not specifically designed with type
inference in mind -- does not possess a type system that allows much
useful information to be derived about variables based on how they are
\textit{used}; only on how they were \textit{produced}.  For example,
a number of very different built-in types can be involved in an
addition; the meaning of the addition and the type of the result
depends on the type of the input arguments.  Merely knowing that a
variable will be used in an addition does not give much information
per se.  For this reason, our annotator works by flowing types
forward, operation after operation, i.e.\ by performing abstract
interpretation of the flow graphs.  In a sense, it is a more naive
approach than the one taken by type systems specifically designed to
enable more advanced inference algorithms.  For example,
Hindley-Milner type inference works in an inside-out direction, by
starting from individual operations and propagating type constraints
outwards \cite{DaMi}\cite{Miln}.

@@

The tool-chain has been tested with and can sucessfully apply
transformations enabling various combinations of features. The
translated interpreters are benchmarked using pystone (a Dhrystone 2.0
\cite{dhry20} derivative traditionally used by the Python community, although it is
a rather poor benchmark) and the classical [Richards] benchmark and
compared against [CPython] 2.4.3 results and are summarized in table
\ref{perfsumm}.

@@

{\bf pypy-c.}
    The simplest variant: translated to C code with no explicit memory
    management, and linked with the Boehm conservative GC.

@@

The resulting generating extension will be essentially similar to
Psyco \cite{psyco}, which is the only (and hand-written) JIT available for Python
so far, based on run-time specialization.

@@

Jikes RVM \cite{jalapeno} is a
Java VM and Just-In-Time compiler written in Java.
Bootstrapping happens by self-applying the compiler on a host VM, and
dumping a snapshot from memory of the resulting native code.
This approach directly enables high performance, at the price of
portability -- as usual with pure native code emitting
approaches. Modularity of features, when possible, is achieved with
normal software modularity. The indirection costs are taken care of by
the compiler performing inlining (which is sometimes even explicitly
requested).  In particular this modular approach is used
for implementing a range of choices for GC support \cite{JikesGC}.  This was
the inspiration for PyPy's own GC framework, although much more tuning
and work went into Jikes RVM.  PyPy's own GC framework also exploits
inlining of helpers and barriers to recover performance.
